Genetic Algorithm Based Formula Generation for Curve Fitting in Time Series Forecasting Implemented as Mobile Distributed Computing

### 2019-05-14 Genetic-Algorithm-Based-Formula-Generation-for-Curve-Fitting-in-Time-Series-Forecasting-Implemented-as-Mobile-Distributed-Computing/paper.tex
Some experimental results were added.

Experiments are done as Android mobile application. On the client side Apache Commons Genetic Algorithms Framework \cite{apache01} is used. Mathematical expressions are presented and evaluated with Java build of mXparser \cite{gromada01} software library. On the server side PHP/MySQL based solution \cite{balabanov03} is responsible for synchronization and financial time series data supply.

>>>>

Experiments are done as Android mobile application. On the client side Apache Commons Genetic Algorithms Framework \cite{apache01} is used with the parameters listed in Tab. \ref{tab01}. Mathematical expressions are presented and evaluated with Java build of mXparser \cite{gromada01} software library. On the server side PHP/MySQL based solution \cite{balabanov03} is responsible for synchronization and financial time series data supply.

\begin{figure}
\includegraphics[width=1.0\textwidth]{fig01.png}
\centering
\caption{EUR/USD rate for two months.} \label{fig01}
\end{figure}

Publicly available data are used for EUR/USD rate for two months in 2019 year (Fig. \ref{fig01}). Bars in the chart shows the real world price. The line above the bars is the line of the formula generated by the proposed genetic algorithm.

\begin{table}[]
\centering
\begin{tabular}{@{}ll@{}}
\hline
\multicolumn{1}{|c|}{{ \textbf{Parameter}}} & \multicolumn{1}{|c|}{{\textbf{Value}}} \\
\hline
\multicolumn{1}{|l|}{generation gap}                                                  & \multicolumn{1}{l|}{0.97}                                                         \\
\multicolumn{1}{|l|}{crossover rate}                                                  & \multicolumn{1}{l|}{0.95}                                                         \\
\multicolumn{1}{|l|}{mutation rate}                                                   & \multicolumn{1}{l|}{0.03}                                                         \\
\multicolumn{1}{|l|}{maximum generations}                                             & \multicolumn{1}{l|}{100}                                                         \\
\multicolumn{1}{|l|}{number of individuals}                                           & \multicolumn{1}{l|}{37}                                                           \\
\multicolumn{1}{|l|}{number of variables}                                             & \multicolumn{1}{l|}{floating}                                                     \\
\multicolumn{1}{|l|}{inserted rate}                                                                       & \multicolumn{1}{l|}{100 \%}                                                                            \\
\hline
\end{tabular}
\caption{Genetic algorithm parameters.}
\label{tab01}
\end{table}
